---
title: "COVID19  - regional statistics"
author: "Richard Martin-Nielsen"
output:
  html_document:
    fig_width: 6
    fig_height: 4
    df_print: paged
    self_contained: false
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
Sys.setenv(`_R_S3_METHOD_REGISTRATION_NOTE_OVERWRITES_` = "false")
library(dplyr)
#library(RtD3)
library(lubridate)
library(htmltools)
library(covidregionaldata)
#library(rmapshaper)

countryName <- "Canada"
activeArea <- "Ontario"
```
Header text also goes here.

``` {r }
# RtD3::summaryWidget(
#   geoData = geoData,
#   rtData = rtData,
#   runDate = max(rtData$Cases$obsCasesData$date)+1,
#   activeArea = 'Vilniaus m.'
#)



HTML('<script src="site_libs/header-attrs-2.7/header-attrs.js"></script>',
  '<script src="site_libs/jquery-3.5.1/jquery.min.js"></script>',
  '<meta name="viewport" content="width=device-width, initial-scale=1" />',
  '<link href="site_libs/bootstrap-3.3.5/css/flatly.min.css" rel="stylesheet" />',
  '<script src="site_libs/bootstrap-3.3.5/js/bootstrap.min.js"></script>',
  '<script src="site_libs/bootstrap-3.3.5/shim/html5shiv.min.js"></script>',
  '<script src="site_libs/bootstrap-3.3.5/shim/respond.min.js"></script>',
  '<script src="site_libs/htmlwidgets-1.5.3/htmlwidgets.js"></script>\n',
    '<script src=\"site_libs/RtD3-binding-0.0.1/RtD3.js\"></script>\n',
     '<link href="site_libs/rtVis-1/styles.css" rel="stylesheet" />\n',
     '<script src="site_libs/rtVis-1/build.min.js"></script>\n',
     '<script src="site_libs/d3-geo-projection-2.9.0/d3-geo-projection.v2.min.js"></script>\n',
     '<script src="site_libs/d3-5.16.0/d3.v5.min.js"></script>\n',
     '<link href="site_libs/select2-4.1.0/select2.min.css" rel="stylesheet" />',
     '<script src="site_libs/select2-4.1.0/select2.min.js"></script>',
      "<div id=\"root\"></div>\n<script>\n",
         "var x = {\n",
            paste0("'activeArea':'", activeArea, "',"),
            "'activeData':'R0',",
            "'activeTime':'all',",
            paste0("'geoData':d3.json('epinow/", countryName, "_regions.geojson'),"),
            "'rtData': {'Cases':{'summaryData':d3.csv('epinow/summary_table.csv'),'rtData':d3.csv('epinow/rt.csv'),'casesInfectionData':d3.csv('epinow/cases_by_infection.csv'),'casesReportData':d3.csv('epinow/cases_by_report.csv'),'obsCasesData':d3.csv('epinow/reported_cases.csv')}},",
            "'fullWidth':800,",
            "'downloadUrl':'http://projects.martin-nielsen.ca/Graphs/data-download.html',",
            "'ts_color_ref':{'poly_90_e':'#d1ebe3','poly_90_eb':'#f7dfcc','poly_90_f':'#e3e2ef','poly_50_e':'#9bd4c2','poly_50_eb':'#edb98f','poly_50_f':'#c2c0dd','poly_20_e':'#75c4ab','poly_20_eb':'#e69e65','poly_20_f':'#aba8d0'},\n}\n",
          "var vis = new rtVis(x, 100, 100);\n",
          "vis.summaryWidget('#root')\n",
          "</script>\n<p>&nbsp;</p>\n")

dataset_details <- get_available_datasets("regional") %>% filter(grepl(countryName, origin))
```

## Credits

```{r intro-credits, results="asis", echo=FALSE}

  cat("Data is sourced using the \n",
    "[covidregionaldata](https://epiforecasts.io/covidregionaldata) package to\n",
    "download data published by\n[",
    dataset_details$source_text,
    "](",
    dataset_details$source_url,
    ").\n\n")

```

The data has been processed using the [EpiNow2](https://epiforecasts.io/EpiNow2/dev/index.html) R package to estimate the time-varying reproduction number, rate of spread, and doubling time. EpiNow2 uses a range of open-source tools ([Abbott et al.](https://doi.org/10.12688/wellcomeopenres.16006.1)), and current best practices ([Gostic et al.](https://doi.org/10.1101/2020.06.18.20134858)). 

The visualisation is built using the [RtD3](https://epiforecasts.io/RtD3/) package following the example given for subnational results.

## References

* Sam Abbott, Joel Hellewell, Katharine Sherratt, Katelyn Gostic, Joe Hickson, Hamada S. Badr, Michael DeWitt, Robin Thompson, EpiForecasts, and Sebastian Funk (2020). EpiNow2: Estimate Real-Time Case Counts and Time-Varying Epidemiological Parameters, DOI: 10.5281/zenodo.3957489
* Hamish Gibbs (2020). RtD3: Rt Visualization in D3, DOI: 10.5281/zenodo.4011841
